The trend in asymmetric drift across the blue cloud

### 2017-02-16 ms.tex
added massive bibtex repo

\input{../dm_nomenclature/dmnom_rv4.tex}

@@

We model the geometric projection of the rotational plane of each galaxy
using the approach presented by Andersen \& Bershady (2013); see also
Westfall et al. (2011).  In three independent fitting iterations, the
model fits are optimized for the H$\alpha$ velocity field, the stellar
velocity field, and simultaneously for both data sets; for the latter,
the geometry is forced to be the same for the two dynamical tracers, but
the parametrized rotation curves are independent.  We use these
velocity-field-fitting results to objectively isolate a set of
``kinematically regular'' galaxies.  Briefly, galaxies in this sample
must have: (i) successful velocity-field fits for all three approaches,
(ii) differences in the measured H$\alpha$ and stellar systemic velocity
of less than 20 \kms, (iii) dynamical centers that are consistent to
within a fiber diameter of the morphological center [[check]], (iv)
H$\alpha$ and stellar velocity-field position angles that are consistent
to within $\pm$15$\arcdeg$, and (v) kinematic inclinations between
$15\arcdeg < i < 80\arcdeg$ that are both consistent between the
H$\alpha$ and stellar data and with respect to the photometric
ellipticity to within $\pm$20$\arcdeg$.  The constraint on the
inclination is by far the most stringent. [[give number of galaxies cut
by each criterion?]]  Applying these constraints yields a sample of 798
observations (for 790 unique galaxies) out of the 2764 observations
analyzed.  Eleven galaxies with repeat observations satisfy the
selection criteria; however, only five of these show all observations
are consistently selected, whereas the other six show one or more of the
observations did not pass our constraints [[we should understand
this.]].  [[TBD: Finally, we also visually inspected the broad-band
imaging of these 790 galaxies and eliminated merging and highly
extincted (highly inclined) systems yielding a final sample of XXX
galaxies.]]  We hereafter refer to galaxies that satisfy our selection
criteria as the ``asymmetric-drift'' sample.

@@

\bibliography{../master}

>>>>

%\input{../dm_nomenclature/dmnom_rv4.tex}

@@

We model the geometric projection of the rotational plane of each galaxy
using the approach presented by Andersen \& Bershady (2013); see also
Westfall et al. (2011).  In three independent fitting iterations, the
model fits are optimized for the H$\alpha$ velocity field, the stellar
velocity field, and simultaneously for both data sets; for the latter,
the geometry is forced to be the same for the two dynamical tracers, but
the parametrized rotation curves are independent.  We use these
velocity-field-fitting results to objectively isolate a set of
``kinematically regular'' galaxies.  Briefly, galaxies in this sample
must have: (i) successful velocity-field fits for all three approaches,
(ii) differences in the measured H$\alpha$ and stellar systemic velocity
of less than 20 km/s, (iii) dynamical centers that are consistent to
within a fiber diameter of the morphological center [[check]], (iv)
H$\alpha$ and stellar velocity-field position angles that are consistent
to within $\pm$15$\arcdeg$, and (v) kinematic inclinations between
$15\arcdeg < i < 80\arcdeg$ that are both consistent between the
H$\alpha$ and stellar data and with respect to the photometric
ellipticity to within $\pm$20$\arcdeg$.  The constraint on the
inclination is by far the most stringent. [[give number of galaxies cut
by each criterion?]]  Applying these constraints yields a sample of 798
observations (for 790 unique galaxies) out of the 2764 observations
analyzed.  Eleven galaxies with repeat observations satisfy the
selection criteria; however, only five of these show all observations
are consistently selected, whereas the other six show one or more of the
observations did not pass our constraints [[we should understand
this.]].  [[TBD: Finally, we also visually inspected the broad-band
imaging of these 790 galaxies and eliminated merging and highly
extincted (highly inclined) systems yielding a final sample of XXX
galaxies.]]  We hereafter refer to galaxies that satisfy our selection
criteria as the ``asymmetric-drift'' sample.

@@

\bibliography{master}
